---
title: "assignment_2b"
author: "Allison Bailey, Bri Baker, Cameryn Brock"
date: "2/22/2021"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(ggpubr)

```

```{r}
source("power_fun.R")
```

# Possible occurances on our highway

##Four car types 

* Car A: mass 20000 kg, area 22 m^2^

* Car B: mass 65000 kg, area 30 m^2^

* Car C: mass 38000 kg, area 22 m^2^

* Car D: mass 30000 kg, area 10 m^2^

*Mean highway speed is 100 km/hr*


```{r possible cars, eval=TRUE, echo=TRUE}

# generate df of possible cars
possible_cars = data.frame(
  name = c("A","B","C","D"),
  mass=c(10000,65000,38000,30000), 
  area = c(22,30,22,10))

```


## Sampling 100 random highways

```{r highway sample}

# random sample fo 100 highways with different rolling coefficients
c_rolling = runif(min=0.01, max=0.03, n=100)

```



# `for()` loop calculation

Here we utilize a `for()` loop to compute the power for each of 100 different highways for each car in *possible_cars* assuming a single speed of 120 km/hr.

```{r for loop calc}

#set up df
for_loop_calc = as.data.frame(matrix(nrow=length(c_rolling), ncol=nrow(possible_cars)))
#


for (i in 1:nrow(possible_cars)) { 
  for_loop_calc[,i] = power_fun(a=possible_cars$area[i], m=possible_cars$mass[i], v=120*.28, c_r = c_rolling)
  
}


```

```{r}
car_power_loop = for_loop_calc %>% 
  pivot_longer(cols=everything(), names_to="car", values_to="power")

```

```{r for box}
##box plot of power consumed for each car type (where the boxes will show ranges across the different highways

for_plot <- ggplot(car_power_loop, aes(car, power, fill=car))+
  geom_boxplot()+
  ggtitle("For Loop")+
  labs(y="Power (watts)",
       x="Cars")

for_plot

```



# `pmap()` calculation

Here we utilize `pmap()`  to compute the power for each of 100 different highways for each car in *possible_cars*, again assuming a single speed of 120 km/hr.

```{r pmap calc}

pmap_calc <- pmap(list(a=possible_cars$area, m=possible_cars$mass), power_fun, v=120*.28, c_r=c_rolling) 
  
pmap_df <- pmap_calc %>%
  as.data.frame(col.names = possible_cars$name) %>% 
  pivot_longer(cols=everything(), 
               names_to="car", 
               values_to="power")
  
  

```

```{r pmap box}
##box plot of power consumed for each car type (where the boxes will show ranges across the different highways

pmap_plot <- ggplot(pmap_df, aes(car, power, fill=car))+
  geom_boxplot()+
  ggtitle("pmap") +
   labs(y="Power (watts)",
       x="Cars")

pmap_plot

```


