---
title: "assignment_2b"
author: "Allison Bailey"
date: "2/22/2021"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(ggpubr)

```

```{r}
source("power_fun.R")
```

# Possible occurances on our highway

##Four car types 

* Car A: mass 20000 kg, area 22 m^2^

* Car B: mass 65000 kg, area 30 m^2^

* Car C: mass 38000 kg, area 22 m^2^

* Car D: mass 30000 kg, area 10 m^2^

*Mean highway speed is 100 km/hr*


```{r possible cars, eval=TRUE, echo=TRUE}

# generate df of possible cars
possible_cars = data.frame(
  name = c("A","B","C","D"),
  mass=c(10000,65000,38000,30000), 
  area = c(22,30,22,10))

```


## Sampling 100 random highways

```{r highway sample}

# random sample fo 100 highways with different rolling coefficients
c_rolling = runif(min=0.01, max=0.03, n=100)

```



# `for()` loop calculation

Here we utilize a `for()` loop to compute the power for each of 100 different highways for each car in *possible_cars* assuming a single speed of 120 km/hr.

```{r for loop calc}

#set up df

#

for (variable in vector) {
  
}


```

```{r for box}
##box plot of power consumed for each car type (where the boxes will show ranges across the different highways

for_plot <- ggplot(DATA, aes(car, power, fill=car))+
  geom_boxplot()+
  ggtitle("For Loop")

```



# `pmap()` calculation

Here we utilize `pmap()`  to compute the power for each of 100 different highways for each car in *possible_cars*, again assuming a single speed of 120 km/hr.

```{r pmap calc}

pmap_calc <- pmap(list(changing variables), static variables) #%>% 
  as.data.frame(col.names = ) #%>% 
  pivot_longer(cols=everything(), 
               names_to="car", 
               values_to="power")

```

```{r pmap box}
##box plot of power consumed for each car type (where the boxes will show ranges across the different highways

pmap_plot <- ggplot(DATA, aes(car, power, fill=car))+
  geom_boxplot()+
  ggtitle("pmap")

```




-------below here is reference info, delete after completion-------




```{r withpmap}

# the first part, generating speeds is the same
# what is I want to estimate average power use given  each car

possible_cars

# the first part is the same as above
# use sample to generate a distribution of speeds

# assume a log normal distribution of speeds with mean 100km/hr
# recall our function needs speed in m/s not km/hr so we will also do a conversion
# lets get a sample of a 200 speeds- we could also do this by actually measuring speeds

nsample = 200
mean_speed = log(100*0.277)

speeds = rlnorm(mean=mean_speed, sd=0.1*mean_speed, nsample)
summary(speeds)

plot(density(speeds), ylab="Distribution of Speeds in (m/s)")


# how do we run each car for all speeds 
# pmap runs a function for each value in a list of parameters, with other parameters set for each iteration


powerall2 = pmap(list(A = possible_cars$area, m=possible_cars$mass), autopower, V=speeds)

# lets turn to a data frame for easier graphing
# we can add column names
powerall2 = as.data.frame(powerall2, col.names=possible_cars$name)


# for plotting sometimes its useful to turn columns in to rows
powerallr2 = powerall2 %>% pivot_longer(cols=everything(), names_to="car", values_to="power")
head(powerallr2)

# quick visualization

method2_plot = ggplot(powerallr2, aes(car,power, fill=car))+geom_boxplot()+ggtitle("pmap")
method2_plot


```

# Third - classic looping *for*

*pmap* works quickly but it is unique to R
Other programming language (and R) use what are called loops - where repetition is more explicit

Lets do this one more time using a *for* loop

```{r withforloop}

# the first part, generating speeds is the same
# what is I want to estimate average power use given  each car

possible_cars

# use sample to generate a distribution of speeds

# assume a log normal distribution of speeds with mean 100km/hr
# recall our function needs speed in m/s not km/hr so we will also do a conversion
# lets get a sample of a 200 speeds- we could also do this by actually measuring speeds

nsample = 200
mean_speed = log(100*0.277)

speeds = rlnorm(mean=mean_speed, sd=0.1*mean_speed, nsample)
summary(speeds)

plot(density(speeds), ylab="Distribution of Speeds in (m/s)")


# how do we run each car for all speeds 
# we use a for loop to cycle through
# we need to create a data frame to store results - as above
# one column for each car and one row for each speed

powerall3 = as.data.frame(matrix(nrow=length(speeds), ncol=nrow(possible_cars)))
# because we don't initialize it - values are NA
head(powerall3)

# how many cars area there
nrow(possible_cars)
# for loops use an index - in this case "i" but you could use anything - it repeats
# anything between the {} for each values of i between 1 and nrow(possible_car) (which is 3 in our case)

# index in to a matrix (like powerall3) is by row and column powerall3[2,5] is 2nd row and 5th column
for (i in 1:nrow(possible_cars)) {
  powerall3[,i] = autopower(A=possible_cars$area[i], m=possible_cars$mass[i], V=speeds)
}

# now it looks like above
head(powerall3)
# we can add column names
colnames(powerall3)=possible_cars$name

# plotting is the same as above

# for plotting sometimes its useful to turn columns in to rows
powerallr3 = powerall3 %>% pivot_longer(cols=everything(), names_to="car", values_to="power")
head(powerallr3)

# quick visualization
method3_plot = ggplot(powerallr3, aes(car,power, fill=car))+geom_boxplot()+ggtitle("For Loop")

ggarrange(method1_plot, method2_plot, method3_plot, nrow=3)

powerall1 %>% map(mean)
powerall2 %>% map(mean)
powerall3 %>% map(mean)

```

