---
title: "assignment_3"
author: "Allison Bailey"
date: "2/25/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Lightening Activity Levels

The National Park Service designates Lightening Activity Levels to monitor potential fires and manage recreation.  

Lightening Activity Level is rated on a scale of 1 to 6 as described below:
  
LAL 1— No thunderstorm or building cumulus clouds observed.

LAL 2— A single or few building cumulus clouds with only an occasional one reaching thunderstorm intensity observed. Thunderstorms or lightning need not be observed for this activity level to be assigned; however at least one large cumulus cloud must be present.

LAL 3— Occasional lightning (an average of 1 to 2 cloud -to-ground strikes per minute) is observed. Building cumulus clouds are common; thunderstorms are widely scattered.

LAL 4— Frequent lighting (an average of 2 to 3 cloud-to-ground strikes per minute) is observed. Thunderstorms are common and cover 10 to 30 percent of the sky. Lightning is primarily of the cloud-to-cloud type but cloud-to-ground lightning may be observed.

LAL 5— Frequent and intense lightning (cloud-to-ground strikes greater than 3 per minute) is observed. Thunderstorms are common, occasionally obscuring the sky. Moderate to heavy rain usually precede and follow the lightning activity. Lightning of all kinds (cloud-to-cloud, in-cloud and cloud-to-ground) is characteristically persistent during the storm period.

LAL 6— A dry lightning situation. Low lightning flash rate observed (less than one to three cloud-to-ground strikes per 5-minute period per storm cell passage). Scattered towering clouds with a few thunderstorms; bases of the clouds are high. Virga is the predominate form of precipitation.

Source: National Park Service - https://www.nps.gov/articles/understanding-fire-danger.htm

```{r, include=FALSE, message=FALSE, warning=FALSE}
# Bring in tidyverse to run the LAL functions.

library(tidyverse)

```


```{r}
# Numeric Fire Levels created with "while()"

source("lightening_levs.R")

```

```{r}
# Fire Level Definitions created with "case_when()"

source("lal_cased.R")

```

